\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-15 experience.tex
updates in case studies

\section{Additional Example I: Live Azure Table Migration}
\label{sec:cases:migration}

The Live Azure Table Migration is a library capable of transparently migrating a data set between tables in the Windows Azure storage service while an application is accessing the data set.  MigratingTable provides a \emph{virtual table} with an API similar to that of an ordinary Azure table, backed by a pair of \emph{old} and \emph{new} tables.  A background \emph{migrator} job moves all data from the old table to the new table.  Meanwhile, each read or write issued to the virtual table is translated to a sequence of reads and writes on the backend tables according to a protocol we designed, which guarantees linearizability of operations on the virtual table across multiple application processes assuming that the backend tables respect their own linearizability guarantees.

@@

% N.B. Artifact Services is mentioned at http://research.microsoft.com/en-us/people/schulte/.  Hopefully it's OK to reveal that it was the system in this case study. ~ Matt 2015-08-17
The initial motivation for MigratingTable was to solve a scaling problem for Artifact Services, an internal Microsoft system with a data set that is sharded across tables in different Azure storage accounts because it exceeds the limit on traffic supported by a single Azure storage account.  As the traffic continues to grow over time, the system needs to reshard the data set across a greater number of Azure storage accounts without interrupting service.  During such a resharding, our sharding manager will identify each key range that should migrate to a different table, and we will use a separate MigratingTable instance for each such key range to actually perform the migration (Figure~\ref{fig:livemigration}).  MigratingTable may also be useful to migrate data to a table with different values of configuration parameters that Azure does not support changing on an existing table, such as geographic location.

\def\term#1{\emph{#1}}
We also used \psharp to test the MigratingTable library, which is capable of transparently migrating a data set between tables in the Windows Azure storage service while an application is accessing the data set.

@@

MigratingTable implements an interface called IChainTable2, which provides the core read and write functionality of the original Azure table API with one exception: it provides \term{streaming reads} with a weaker consistency property than multi-page reads in the original API, since the original property would have been difficult to achieve for no benefit to applications we could foresee.  MigratingTable requires that its backend tables also implement IChainTable2, and we wrote a simple adapter to expose physical Azure tables as IChainTable2.  Our goal was then to verify that when multiple application processes issue ``input'' read and write calls to their own MigratingTable instances with the same backend tables, the behavior complies with the specification of IChainTable2 for the combined input history.

@@

As mentioned above, the IChainTable2 specification is almost deterministic under sequential calls; the only nondeterminism is in the results of streaming reads.  Given a streaming read, SpecTable can compute the set of all results that are compliant with the specification, so we can simply check if the result of MigratingTable is in this set.  To test MigratingTable, we must supply it with backing tables.  We use SpecTable for this purpose as well, with \psharp choosing the actual result of each streaming read from the valid set.  Our correctness property is then:
% Convert to some theorem-like environment? ~ Matt
\begin{quote}
For every execution trace of a collection of MigratingTables backed by the same pair of \term{old} and \term{new} SpecTables in parallel with the migrator job, there exists a linearization of the combined input history such that the output in the original trace matches the output of a ``reference'' SpecTable on the linearized input.
\end{quote}
%
We instrumented MigratingTable to report the intended \term{linearization point} of each input call, which in our setting is always one of the corresponding \term{backend calls} to the backend tables (often the last).  Specifically, after each backend call completes, MigratingTable reports whether that call was the linearization point, which may depend on the result of the call.  This makes it possible to verify the correctness property as the model executes.  The model consists of a \psharp \term{tables machine} containing all three SpecTables; a collection of \term{service machines} containing identically configured MigratingTables; and a \term{migrator machine} that performs the background migration (Figure~\ref{fig:mockedmigration}).  Each service machine issues a random sequence of input calls to its MigratingTable, which sends backend calls to the tables machine.  When MigratingTable reports the linearization point of an input call, the service machine sends that input call to the reference table.  When an input call completes, the service machine checks that the results from the MigratingTable and the reference table agree.  \psharp controls the interleaving of the backend calls.  To ensure that the reference table is never observed to be out of sync with the backend tables, after the tables machine processes a backend call, it enters a state that defers further backend calls until MigratingTable has reported whether the backend call was a linearization point and (if so) the call to the reference table has been made.  We use the \psharp random scheduling strategy; we were afraid that an exhaustive strategy would only be feasible within bounds so low that we would miss some bugs.

@@

\subsection{An example bug in MigratingTable}
\MMComment{Move wherever appropriate}

@@

\MMComment{Add a figure based on migration-bug3-explanation.pptx (probably a hybrid of slides 4 and 5, assuming we want only one figure).}

\section{Additional Example II: Azure Service Fabric (change to CScale?)}
\label{sec:cases:fabric}

\PDComment{I guess we should write stuff about CScale here based on our last discussion: overview of the system (collection of Fabric services connected via TPL dataflow?), of its environment (Fabric), how they interop?, why its very challenging to test? how they test currently? I am not sure if all these should go here or be split here and the experience report, we will see ... same for the above case studies}

>>>>

\section{Additional Case Studies}
\label{sec:cases:other}

The modeling and testing approach described in earlier sections of the paper is not specific to the vNext system. \psharp is a generic framework, capable of handling arbitrary distributed systems. We showcase this capability by presenting developer experience in using \psharp to model and test two other distributed storage systems used in production in Microsoft: the Live Azure Table Migration library; and the Azure Service Fabric system.

\subsection{Live Azure Table Migration}
\label{sec:cases:migration}

- Advanced safety properties\\
- Handles intra-machine concurrency\\
- Writing the protocol while testing it (co-development)

The Live Azure Table Migration (MigratingTable) is a library for transparently migrating a data set between tables in an Azure Storage service, while an application is accessing this data set.

MigratingTable provides a \emph{virtual table} with an API similar to that of an ordinary Azure table, backed by a pair of \emph{old} and \emph{new} tables.  A background \emph{migrator} job moves all data from the old table to the new table.  Meanwhile, each read or write issued to the virtual table is translated to a sequence of reads and writes on the backend tables according to a protocol that guarantees linearizability of operations on the virtual table across multiple application processes, assuming that the backend tables respect their own linearizability guarantees.

@@

% N.B. Artifact Services is mentioned at http://research.microsoft.com/en-us/people/schulte/.  Hopefully it's OK to reveal that it was the system in this case study. ~ Matt 2015-08-17
%The initial motivation for MigratingTable was to solve a scaling problem for Artifact Services, an internal Microsoft system with a data set that is sharded across tables in different Azure storage accounts because it exceeds the limit on traffic supported by a single Azure storage account.  As the traffic continues to grow over time, the system needs to reshard the data set across a greater number of Azure storage accounts without interrupting service.  During such a resharding, our sharding manager will identify each key range that should migrate to a different table, and we will use a separate MigratingTable instance for each such key range to actually perform the migration (Figure~\ref{fig:livemigration}).  MigratingTable may also be useful to migrate data to a table with different values of configuration parameters that Azure does not support changing on an existing table, such as geographic location.

@@

MigratingTable implements an interface called IChainTable2, which provides the core read and write functionality of the original Azure table API with one exception: it provides \emph{streaming reads} with a weaker consistency property than multi-page reads in the original API, since the original property would have been difficult to achieve for no benefit to applications we could foresee.  MigratingTable requires that its backend tables also implement IChainTable2, and we wrote a simple adapter to expose physical Azure tables as IChainTable2.  Our goal was then to verify that when multiple application processes issue ``input'' read and write calls to their own MigratingTable instances with the same backend tables, the behavior complies with the specification of IChainTable2 for the combined input history.

@@

As mentioned above, the IChainTable2 specification is almost deterministic under sequential calls; the only nondeterminism is in the results of streaming reads.  Given a streaming read, SpecTable can compute the set of all results that are compliant with the specification, so we can simply check if the result of MigratingTable is in this set.  To test MigratingTable, we must supply it with backing tables.  We use SpecTable for this purpose as well, with \psharp choosing the actual result of each streaming read from the valid set.  Our correctness property is then:
% Convert to some theorem-like environment? ~ Matt
\begin{quote}
For every execution trace of a collection of MigratingTables backed by the same pair of \emph{old} and \emph{new} SpecTables in parallel with the migrator job, there exists a linearization of the combined input history such that the output in the original trace matches the output of a ``reference'' SpecTable on the linearized input.
\end{quote}
%
We instrumented MigratingTable to report the intended \emph{linearization point} of each input call, which in our setting is always one of the corresponding \emph{backend calls} to the backend tables (often the last).  Specifically, after each backend call completes, MigratingTable reports whether that call was the linearization point, which may depend on the result of the call.  This makes it possible to verify the correctness property as the model executes.  The model consists of a \psharp \emph{tables machine} containing all three SpecTables; a collection of \emph{service machines} containing identically configured MigratingTables; and a \emph{migrator machine} that performs the background migration (Figure~\ref{fig:mockedmigration}).  Each service machine issues a random sequence of input calls to its MigratingTable, which sends backend calls to the tables machine.  When MigratingTable reports the linearization point of an input call, the service machine sends that input call to the reference table.  When an input call completes, the service machine checks that the results from the MigratingTable and the reference table agree.  \psharp controls the interleaving of the backend calls.  To ensure that the reference table is never observed to be out of sync with the backend tables, after the tables machine processes a backend call, it enters a state that defers further backend calls until MigratingTable has reported whether the backend call was a linearization point and (if so) the call to the reference table has been made.  We use the \psharp random scheduling strategy; we were afraid that an exhaustive strategy would only be feasible within bounds so low that we would miss some bugs.

@@

\subsubsection{An example bug in MigratingTable}

@@

\subsection{Azure Service Fabric}
\label{sec:cases:fabric}

- \psharp generalized beyond vNext. \psharp is not only applicable to vNext but in many systems.\\
- (Advanced) safety properties?\\
- What we developed is a model that other people can reuse. Plugin the model and test the user application.\\
- Example of advanced modeling capability of \psharp. One component talks to another sophisticated API. We demonstrate environmental modeling expressivity in system engineering.
